---
title: "PregnancyPaper_BehaviouralAnalysis"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Project: Pregnancy Paper
Authors: Shasta Webb, Joseph Orkin, Rachel Williamson, Amanda Melin

### Behavioural Analysis

#### Loading required packages and dependencies

```{r}
library(readr)
library(tidyr)
library(dplyr)
library(car)
library(ggplot2)
library(lme4)
library(broom)
library(emmeans)
library(multcomp)
library(multcompView)
library(gridExtra)
library(fuzzyjoin)
```

#### Reading in UTF-8 encoded CSVs from iCloud Desktop

2016, 2017, 2018 behavioural data are currently saved in 3 separate files. 

#### 2016 filtering

The reproductive status information still needs to be added to the data. Here we will sort out all the females, combine the data into one dataframe, then add reproductive status info in Excel. Once that data is sorted, we will then add fruit biomass data and color vision phenotypes back in using R. 

```{r}
df16 <- read.csv('BehaviouralData/BehaviorData/CSVs/2016_BehData.csv')
df16 <- data.frame(df16, stringsAsFactors = FALSE)
females2016 <- c("SS", "CH", "OR", "CE", "SF", "TH", "VN", "SJ", "SI", "ED", "KI", "SH", "LU", "FT", "LA", "PR", "ZA", "BO", "AB", "PT", "RS", "PD", "QD", "WK", "SP", "LM", "TS", "MI", "BT", "LL", "MW")

dff2016 <- df16 %>%
            filter(Animal %in% females2016) %>%
            drop_na(TempMax, TempMin, Rainfall_cm)

dff2016 %>% group_by(Animal, Group) %>% summarise()
```
  
#### 2017 filtering

```{r}
df17 <- read.csv('BehaviouralData/BehaviorData/CSVs/2017_BehData.csv')
df17 <- data.frame(df17, stringsAsFactors = FALSE)
females2017 <- c("BO", "AB", "TS", "LM", "MI", "BT", "ZA", "SI", "LU", "PR", "FT", "SH", "KI", "ED", "LA", "PT", "LL", "QD", "PD", "WK", "RS", "SP", "MW", "SS", "OR", "TH", "SJ", "CE", "VN", "CH")

dff2017 <- df17 %>%
            filter(Animal %in% females2017) %>%
            drop_na(TempMax, TempMin, Rainfall_cm)
```

#### 2018 filtering

```{r}
df18 <- read.csv('BehaviouralData/BehaviorData/CSVs/2018_BehData.csv') 
df18 <- data.frame(df18, stringsAsFactors = FALSE)
females2018 <- c("PT", "LL", "QD", "PD", "HI", "NP", "SP", "WK", "RS", "MW", "BO", "TS", "AB", "LM", "BT", "MI", "ZA")

dff2018 <- df18 %>%
            filter(Animal %in% females2018) %>%
            drop_na(TempMax, TempMin, Rainfall_cm)

dff2018 <- rename(dff2018, DateOf = Date) #renaming the column names so all three years match
```

#### Merging filtered datasets

Here we are combining the three dataframes. The result is one larger dataframe with 1631 rows, each representing a single day of data collection per monkey. 

```{r}
combinedDF <- rbind(dff2016, dff2017)
combinedDF <- rbind(combinedDF, dff2018)
combinedDF[is.na(combinedDF)] <- 0 
#View(combinedDF) #1631 rows
```

Let's use distinct() to ensure that we only have the monkeys in the groups they should be in. 

```{r}
length(unique(combinedDF$Animal)) #33 females
testCdf <- combinedDF %>%
            distinct(Animal, Group) #;View(testCdf)
```

```{r}
combinedDFtest <- combinedDF %>%
                  filter(!(Animal == "LM" & Group == "RM")) %>%
                  filter(!(Animal == "WK" & Group == "AD")) %>%
                  filter(!(Animal == "PD" & Group == "RM")) %>%
                  filter(!(Animal == "OR" & Group == "RM")) %>%
                  filter(!(Animal == "BT" & Group == "LV")) %>%
                  filter(!(Animal == "CH" & Group == "AD")) %>%
                  filter(!(Animal == "BT" & Group == "GN")) %>%
                  filter(!(Animal == "SH" & Group == "LV")) %>%
                  filter(!(Animal == "TS" & Group == "GN"))

df <- combinedDFtest %>%
            distinct(Animal, Group) #this returns only correct animal-group pairings
combinedDF <- combinedDFtest #renaming so that combined DF is the clean one
write.csv(combinedDF, "BehaviouralData/BehaviorData/CSVs/combinedDFclean.csv")
```

#### Reading in combined (clean) dataframe

The above chunks were run originally to generate one combined dataset that has been exported. Now we will read in that csv and proceed with analysis.

```{r}
combinedDF <- read.csv("BehaviouralData/BehaviorData/CSVs/combinedDFclean.csv")
combinedDF <- as.data.frame(combinedDF) #;View(combinedDF) #1618 rows
View(combinedDF)
```

#### Adding rotation numbers

This table was originally extracted from the larger dataset. Extreme rain days (>10cm in 24 hours) were determined and each rotation was given a specific name. Here we will left join on the "DateOf" to add rotation to the combinedDF. During some rotations, babies were born, which changes rep status of a group member. These rotations are signified with an "R" behind the number. This allows for grouping while maintaining distinct rep statuses. 

```{r}
rotationTable <- read.csv("BehaviouralData/BehaviorData/rotationFull.csv")
rotationTable <- as.data.frame(rotationTable)
rotationTable <- rotationTable %>%
                 #dplyr::select(-X) %>%
                 distinct()

combinedDF <- combinedDF %>% #1618 rows
              left_join(., rotationTable, by = c("DateOf" = "Date")) #;View(combinedDF) #ensure that the left join worked correctly and no duplicated rows were produced
```

#### Adding color vision & dominance information to combinedDF

```{r}
#colorVisionTable <- as.data.frame(read.csv("~/Desktop/PregnancyPaper2019/BehaviouralAnalysis/EcologicalDataCensus/ColorVisionPhenotypes.csv"))

#combinedDFcolor <- combinedDF %>% #1618
#              left_join(., colorVisionTable, by = c("Animal" = "AnimalCode")) #;View(combinedDF)

#combinedDF <- combinedDFcolor
```

#### Adding dominance scale data

```{r}
dominanceTable <- read.csv("BehaviouralData/EcologicalDataCensus/DominanceScale16_18.csv")
dominanceTable <- as.data.frame(dominanceTable)

combinedDFdom <- combinedDF %>% #1618
                 fuzzy_left_join(., dominanceTable, 
                              by = c("Animal" = "Animal", "DateOf" = "StartYear", "DateOf" = "EndYear"), #match_fun = 
                              list(`==`, `>=`, `<=`)) #;View(combinedDF)

combinedDF <- combinedDFdom
```

#### Removing columns we don't need, and renaming "Animal.x"

```{r}
combinedDF <- combinedDF %>% #1618 rows
              dplyr::select(-X)
```

#### Adding reproductive statuses

```{r}
repStatusTable <- read.csv("BehaviouralData/EcologicalDataCensus/RepStatusSSRFemalesClean.csv")
repStatusTable <- as.data.frame(repStatusTable)

combinedDFrep <- combinedDF %>% #1618 rows
                  fuzzy_left_join(., repStatusTable, 
                            by = c("Animal" = "AnimalCode", "DateOf" = "StartDate", "DateOf" = "EndDate"), 
                            match_fun = list(`==`, `>=`, `<=`)) ;View(combinedDFrep)

combinedDF <- combinedDFrep
```

#### Removing columns we don't need, and renaming "Animal.x", making a copy

```{r}
combinedDF <- combinedDF %>% #1618 rows
              dplyr::select(-Animal.y, -AnimalCode, -X, -X.1) %>%
              rename(Animal = Animal.x) #;View(combinedDF)
combinedDFCopy <- combinedDF #saving a copy of the correct DF here
```

#### Adding monthly biomass (kg/ha) data

```{r}
fruitBiomassTable <- as.data.frame(read.csv("BehaviouralData/EcologicalDataCensus/MonthlyFruitBiomass.csv"))
fruitBiomassTable <- fruitBiomassTable %>%
                     mutate(MonthOfYear = format(as.Date(YearOf,format="%Y-%m-%d"),"%Y-%m")) 
                    #;View(fruitBiomassTable)

combinedDFfruit <- combinedDF %>% #1618 rows
              mutate(MonthOfYear = format(as.Date(DateOf,format="%Y-%m-%d"),"%Y-%m")) %>%
              left_join(., fruitBiomassTable, by = "MonthOfYear") #;View(combinedDF)

combinedDF <- combinedDFfruit
```

#### Cleaning up columns we don't need

```{r}
combinedDF <- combinedDF %>%
              dplyr::select(-MonthOfYear, -YearOf)
```

#### Mutating ecological variables and turning them to z-transformed data points

This code z-tranforms the ecological variables and stores them in a new dataframe. Z transforming makes the mean of each variable 0, and the standard deviation 1. It introduces considerable stability into the models without compromising any relationships between the two.

```{r}
dfz <- combinedDF %>%
       mutate_at(vars("TempMax", "TempMin", "Rainfall_cm", "MonthlyFruitBiomass_kg_ha"), list(~as.numeric(scale(.)))) 
```

#### Assigning categorical levels to Dominance Scale

```{r}
dfz$DominanceCat <- if_else(
                        dfz$DominanceScale <= 0.33, "low", 
                        if_else(dfz$DominanceScale > 0.33 & 
                        dfz$DominanceScale <= 0.66, "mid","high")) #Dominance rank was converted to dominance scale to make comparisons across groups. Dominance scale was broken into 3 groups, low, mid, and high-ranking.
```

#### Totalling scans & replacing NAs

```{r}
dfz <- dfz %>%
       mutate(TotalRestingScans = rowSums(dplyr::select(., SRE, RES))) %>%
       mutate(TotalRestingScans = ifelse(is.na(TotalRestingScans),0,TotalRestingScans)) %>% #Replacing NAs with 0s
       mutate(TotalForagingScans = rowSums(dplyr::select(. , EFI, FFL, FFR, FIN, FOT, VFO))) %>%
       mutate(TotalForagingScans = ifelse(is.na(TotalForagingScans),0,TotalForagingScans)) %>% #Replacing NAs with 0s
       mutate(TotalInsectForaging = rowSums(dplyr::select(., EFI, VFO, FIN))) %>%
       mutate(TotalInsectForaging = ifelse(is.na(TotalInsectForaging),0,TotalInsectForaging)) %>% #Replacing NAs with 0s
       mutate(TotalScans = rowSums(dplyr::select(., DRI:VIG))) %>%
       mutate(TotalScans = ifelse(is.na(TotalScans),0,TotalScans)) #;View(dfz)

dfz <- dfz %>%
       dplyr::select(-Animal.y, StartYear, EndYear) %>%
       rename(Animal = Animal.x)

dfzArranged <- dfz %>%
               dplyr::select(DateOf, Animal, Rotation, ReproductiveStatus, Group, TempMax, Rainfall_cm, DRI, EFI, EXC, FFL, FFR, FIN, FOT, OTH, PLA, RES, SAC, SAG, SDI, SRE, TRA, VFO, VIG, TotalRestingScans, TotalForagingScans, TotalInsectForaging, TotalScans, Miscarriage, InfantSurvive1Year, InfantSurvive3Years, StartDate, EndDate, DominanceScale, DominanceCat, MonthlyFruitBiomass_kg_ha)

write_csv(dfzArranged, "BehaviouralData/BehaviorData/dfz20august.csv") #saving the updated DF in a new file
```

Since we will be collapsing the data into the different rotations, thereby losing specific date information, we may still want month and year data. 

```{r}
dfz <- read.csv("BehaviouralData/BehaviorData/dfz20august.csv")
dfz <- as.data.frame(dfz)
dfz <- dfz %>% 
      mutate(MonthOfYear = format(as.Date(DateOf,format="%Y-%m-%d"),"%Y-%m"))
#View(dfz) #1618 rows
```

#### Collapsing rotations using group_by() and filtering to 3+ scans per rotation

Grouping the data by Rotation and Animal groups the data into our units of analysis (all data for one animal per rotation). However, we need to use summarize since we have many different types of data, and we want to treat different variables differently. 

```{r}
dfzGrouped <- dfz %>% 
              group_by(Rotation, Animal) %>% #groups data into units of analysis, but doesn't actually change the way the data look
              summarise( 
                        Group = unique(Group),
                        TempMax = mean(TempMax), 
                        Rainfall_cm = mean(Rainfall_cm), 
                        MonthlyFruitBiomass = mean(MonthlyFruitBiomass_kg_ha),
                        DRI = sum(DRI),
                        EFI = sum(EFI),
                        EXC = sum(EXC),
                        FFL = sum(FFL),
                        FFR = sum(FFR),
                        FIN = sum(FIN),
                        FOT = sum(FOT),
                        OTH = sum(OTH),
                        PLA = sum(PLA),
                        RES = sum(RES),
                        SAC = sum(SAC),
                        SAG = sum(SAG),
                        SDI = sum(SDI),
                        SRE = sum(SRE),
                        TRA = sum(TRA),
                        VFO = sum(VFO),
                        VIG = sum(VIG),
                        DominanceScale = mean(DominanceScale),
                        ReproductiveStatus = unique(ReproductiveStatus),
                        TotalInsectForaging = sum(TotalInsectForaging),
                        TotalRestingScans = sum(TotalRestingScans),
                        TotalForagingScans = sum(TotalForagingScans),
                        TotalScans = sum(TotalScans),
                        MonthOfYear = dplyr::first(MonthOfYear)) #if rotations spanned the end of a month, the month the rotation started is included in the grouped df

```

The grouping will help us keep some data, but there are still some monkeys with too little data to include. We'll filter to keep only rows with 3 or more scans.

```{r}
dfzGrouped <- filter(dfzGrouped, TotalScans > 2) #682 rows (now with all changes in rep status during rotations included)
dfzGrouped$DominanceCat <- if_else(dfzGrouped$DominanceScale <= 0.33, "low", if_else(dfzGrouped$DominanceScale > 0.33 & dfzGrouped$DominanceScale <= 0.66, "mid","high")) #turning scale into a categorical variable
dfzGrouped <- dfzGrouped %>%
              mutate(DominanceCat = replace_na(DominanceCat, "low")) #replacing NAs with low rank, since the NAs are from young females who acheived adult status in the year, but were not evaluated based on rank
```

#### Totals for data collection

```{r}
sum(dfzGrouped$TotalScans) #13689 individual scan records (after filtering to 3 scans per monkey per rotation)
length(unique(dfz$DateOf)) #how many contact days? 222
sum(dfzGrouped$TotalScans)/length(unique(dfzGrouped$Animal)) #mean = ~414 scans per animal
```

#### Variance Inflation Factor test for ecological variables. 

This model tests for the variance inflation factor among the ecological variables. A VIF under 2 is considered an acceptable cutoff for correlation of ecological variables. If the score is under 2, the ecological variables can be left in the model. Note that is this model is a Generalized Linear Model, not a GLMM. 

```{r}
RestModel.vif = glm(TotalRestingScans ~ DominanceCat * 
                              ReproductiveStatus +
                              Rainfall_cm +
                              TempMax +
                              MonthlyFruitBiomass +
                              offset(log(TotalScans)), 
                              data = dfzGrouped,
                              family = "poisson")

car::vif(RestModel.vif) #all scores under 2
```

#### Resting model: monkey and ecological variables

- Reponse variable: TotalRestingScans (count data)
- Predictor variables:
  Fixed effects:
    * DominanceCat: This is a scaled variable from 0-1 taken from the ordinal ranking based on January 2016 SSR ranking. Perdita (lowest ranking) was added to RM, and Buzz (lowest ranking) was changed from top rank to bottom rank after ME's takeover of Admin. 
    * ReproductiveStatus: Categorical variable that includes nursing, pregnant, and cycling. There exists another variable ReproductiveStatusMiscarriage that includes a nursing_mc designation for mothers who were observed nursing after losing a pregnancy. 
    * Rainfall_c,: daily rainfall in cm (z-transformed in this model)
    * TempMax: daily max temp in degrees C (z-transformed in this model)
    * TempMin: daily min temp in degreed C (z-transformed in this model)
    * FruitBiomass: monthly fruit biomass taken from PACE database (z-transformed in this model)
  Random Effects:
    * Monkey ID nesting within social group (to account for individual variation)
-Unit of Analysis: Individual day of scan data per animal with behavioural states summed
  
From Urs: "You have to log-transform the offset because you are using a log-link function. Thus, you are actually testing if log(TotalForagingScans) is associated with dominance etc. (but you are not simply log-transforming your counts as you also use a Poisson distribution and not a Gaussian distribution).

However, you have to correct for effort, thus you actually want to know whether TotalForagingScans/TotalScans is associated with dominance etc. I don’t think this is technically correct, but you can imagine that as testing for log(TotalForagingScans/TotalScans) ~ dominance. However, this is not a count anymore. Because log(m/n) = log(m) - log(n), you can transform this formula to log(TotalForagingScans) - log(TotalScans) ~ dominance, and then to log(TotalForagingScans) ~ dominance + log(TotalScans)." 

-Distribution: Poisson 
    The Poisson distribution is an appropriate model if the following assumptions are true.

      * K is the number of times an event occurs in an interval and K can take values 0, 1, 2, …
      * The occurrence of one event does not affect the probability that a second event will occur. That is, events occur independently.
      * The rate at which events occur is constant. The rate cannot be higher in some intervals and lower in other intervals.
      * Two events cannot occur at exactly the same instant.
      * The probability of an event in a small interval is proportional to the length of the interval.
      
```{r}

dfzGrouped$ReproductiveStatus <- factor(dfzGrouped$ReproductiveStatus, levels = c("Cycling", "Pregnant", "Nursing"))

raw.rest.Rep <- ggplot(data = dfzGrouped, aes(x = ReproductiveStatus, y = TotalRestingScans, fill = ReproductiveStatus)) +
                         geom_boxplot(alpha = 4/10, width = 0.5) +
                         scale_fill_manual(values = c("goldenrod1", "darkslategray4", "olivedrab4")) +
                         scale_x_discrete(limit = c("Cycling", "Pregnant", "Nursing"),
                                          labels = c("Cycling", "Pregnant", "Nursing")) +
                         xlab("") + ylab("\n\nResting scans (Raw counts)\n") +
                         geom_jitter(alpha = 3/10, height = 0) +
                         theme_minimal() +
                         theme(legend.position = "none",
                               axis.text.x = element_blank()); raw.rest.Rep
```

```{r}
RestModel <- glmer(TotalRestingScans ~ DominanceCat + 
                              ReproductiveStatus +
                              Rainfall_cm +
                              TempMax +
                              MonthlyFruitBiomass +
                              offset(log(TotalScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"))

summary(RestModel) #General summary of GLMM
drop1(RestModel, test = "Chisq") #Displays overall effects of each fixed effect using Chi-square test
Anova(RestModel) #Alternative summary using Type II Wald chisquare tests

RM.3states.RESULTS <- as.data.frame(Anova(RestModel))
write.csv(RM.3states.RESULTS, "RM.3states.RESULTS.csv")

RM.emm <- emmeans(RestModel, "ReproductiveStatus", type = "response", adjust = "tukey") #Using emmeans package instead of lsmeans
RM.cld <- cld(RM.emm, alpha=0.05,
          Letters=letters,
          adjust="tukey")

RM.emm.plot <- pwpp(RM.emm, method = "pairwise") #Constructs a plot of P values associated with pairwise comparisons of estimated marginal means.
RM.emm.3states <- as.data.frame(pairs(RM.emm))
write.csv(RM.emm.3states, "BehaviouralData/Tables/RM.emm.3states.csv")

RM.plot <- ggplot(RM.cld, aes(x = ReproductiveStatus, y = rate, fill = ReproductiveStatus)) +
           geom_errorbar(aes(ymin  =  rate + SE, ymax  =  rate - SE), width =  0.4, size  =  0.6,  position = position_dodge(width = 0.5)) +
           geom_point(shape = 21, size = 4, position = position_dodge(width = 0.5)) +
           scale_y_continuous(limits = c(0, 7)) +
           scale_fill_manual(values = c("goldenrod1", "darkslategray4", "olivedrab4")) +
           scale_x_discrete(limit = c("Cycling", "Pregnant", "Nursing"),
                            labels = c("Cycling", "Pregnant", "Nursing")) +
           theme_minimal() +
           theme(legend.position = "none",
                 legend.title = element_blank(),
                 axis.title.x = element_text(size = 14),
                 axis.text = element_text(size = 10),
                 #axis.text.x = element_text(angle = 45, hjust = 0.95, vjust = 0.9, size = 12),
                 plot.title = element_text(lineheight=.8, face="bold", hjust = 0.5)) +
           labs(x = "", y = "\n\nResting scans (EMMs)\n") ;RM.plot

#SI_figure_Rest <- ggarrange(raw.rest.Rep, RM.plot,
#                            labels = c("A", "B"),
#                            ncol = 1, nrow = 2, align = "v"); SI_figure_Rest

ggsave("BehaviouralData/Figures/restModel3States.pdf", plot = RM.plot, height = 5, width = 5)

#ggsave("~/Desktop/PregnancyPaper2019/BehaviouralAnalysis/Figures/SI_Figure_Rest.pdf", plot = SI_figure_Rest, width = 4, height = 6)

```

#### Does our alternative model outperform the null model? Yes. 

```{r}
RestModel.x <- glmer(TotalRestingScans ~ DominanceCat + 
                              ReproductiveStatus +
                              Rainfall_cm +
                              TempMax +
                              MonthlyFruitBiomass +
                              offset(log(TotalScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"))

RestModel.x.null <- glmer(TotalRestingScans ~ 
                              offset(log(TotalScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"))


AIC(RestModel.x, RestModel.x.null) #Use AIC to determine which model performs better. Lower AIC score means better performance. 
```

#### Foraging models

##### Raw foraging plot

```{r}
raw.forage.Rep <- ggplot(data = dfzGrouped, aes(x = ReproductiveStatus, y = TotalForagingScans, fill = ReproductiveStatus)) +
                         geom_boxplot(alpha = 4/10, width = 0.5) +
                         scale_fill_manual(values = c("goldenrod1", "darkslategray4", "olivedrab4")) +
                         scale_x_discrete(limit = c("Cycling", "Pregnant", "Nursing"),
                                          labels = c("Cycling", "Pregnant", "Nursing")) +
                         xlab("") + ylab("\n\nForaging scans (Raw counts)\n") +
                         geom_jitter(alpha = 3/10, height = 0) +
                         theme_minimal() +
                         theme(legend.position = "none",
                               axis.text.x = element_blank()); raw.forage.Rep
```

```{r}
ForageModel <- glmer(TotalForagingScans ~ DominanceCat + 
                              ReproductiveStatus +
                              Rainfall_cm +
                              #TempMax + #with this in the model I get this: boundary (singular) fit: see ?isSingular
                              MonthlyFruitBiomass +
                              offset(log(TotalScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"))

summary(ForageModel)
drop1(ForageModel, test = "Chisq")
forageModel3states <- as.data.frame(Anova(ForageModel))
write.csv(forageModel3states, "BehaviouralData/Tables/forageModel3statesRESULTS.csv")
```

#### Plotting the estimated marginal means for the Forage Model

```{r}
ForageModel.emm <- (emmeans(ForageModel, "ReproductiveStatus", type = "response", adjust = "tukey"))
FM.emm.3states <- pairs(ForageModel.emm)
write.csv(FM.emm.3states, "FM.emm.3states.csv")
plot(ForageModel.emm, comparisons = TRUE, alpha = 0.5)
ForageModel.emm.cld.tukey <- cld(ForageModel.emm, alpha = 0.05, Letters = letters, adjust = "tukey")
FM <- ForageModel.emm.cld.tukey

FM.plot <- ggplot(FM, aes(x = ReproductiveStatus, y = rate, fill = ReproductiveStatus)) +
           geom_errorbar(aes(ymin  =  rate + SE, ymax  =  rate - SE), width =  0.4, size  =  0.6,  position = position_dodge(width = 0.5)) +
           geom_point(shape = 21, size = 4, position = position_dodge(width = 0.5)) +
           scale_y_continuous(limits = c(0, 15)) +
           scale_fill_manual(values = c("goldenrod1", "darkslategray4", "olivedrab4")) +
           scale_x_discrete(limit = c("Cycling", "Pregnant", "Nursing"),
                            labels = c("Cycling", "Pregnant", "Nursing")) +
           theme_minimal() +
           theme(legend.position = "none",
                 legend.title = element_blank(),
                 axis.title.x = element_text(size = 14),
                 axis.text = element_text(size = 10),
                 #axis.text.x = element_text(angle = 45, hjust = 0.95, vjust = 0.9, size = 12),
                 plot.title = element_text(lineheight=.8, face="bold", hjust = 0.5)) +
           labs(x = "", y = "\n\nForaging scans (EMMs)\n") ;FM.plot 

#SI_figure_foraging <- ggarrange(raw.forage.Rep, FM.plot,
                                         #labels = c("A", "B"),
                                         #ncol = 1, nrow = 2, align = "v"); SI_figure_foraging

ggsave("BehaviouralData/Figures/SI_figure_foraging3states.pdf", plot = FM.plot, width = 4, height = 4)

```

#### Social activity (nursing) driving decreased foraging in nursing females?

```{r}
SACmodel <- glmer(SAC ~ DominanceCat + 
                              ReproductiveStatus +
                              Rainfall_cm +
                              #TempMax + #with this in the model I get this: boundary (singular) fit: see ?isSingular
                              #MonthlyFruitBiomass +
                              offset(log(TotalScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"),
                              glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))

summary(SACmodel)
drop1(SACmodel, test = "Chisq")
Anova(SACmodel)

SACmodel.emm <- (emmeans(SACmodel, "ReproductiveStatus", type = "response", adjust = "tukey"))
pairs(SACmodel.emm)
plot(SACmodel.emm, comparisons = TRUE, alpha = 0.5)
SACmodel.emm.cld.tukey <- cld(SACmodel.emm, alpha = 0.05, Letters = letters, adjust = "tukey")
SACM <- SACmodel.emm.cld.tukey

SACM.plot <-    ggplot(SACM, aes(x = ReproductiveStatus, y = rate, label = .group)) +
              geom_point(shape = 16, size = 4) +
              geom_errorbar(aes(ymin = rate - SE, ymax = rate + SE), width = 0.2, size = 0.7) +
              scale_y_continuous(limits = c(0, 5)) +
              theme_bw() +
              labs(x = "", y = "Estimated Marginal Means (Mean SAC Scans per Rotation)\n") ;SACM.plot
              #ggtitle("Estimated Marginal Means for Foraging Scans\n in Response to Reproductive Status") +
              #theme(plot.title = element_text(lineheight = .8, face = "bold", hjust = 0.5)) 

```


### Partitioning of Foraging

Insect foraging model

```{r}

dfzGrouped <- dfzGrouped %>%
              mutate(., insectForaging = VFO + EFI + FIN) %>%
              filter(., TotalForagingScans > 0)

insectModel <- glmer(insectForaging ~ #DominanceCat + 
                              ReproductiveStatus +
                              #Rainfall_cm +
                              #TempMax + 
                              #MonthlyFruitBiomass +
                              offset(log(TotalForagingScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"),
                              glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
```

Fruit foraging model 

```{r}
dfzGrouped <- dfzGrouped %>%
              mutate(., fruitForaging = FFR)

fruitModel <- glmer(fruitForaging ~ DominanceCat + 
                              ReproductiveStatus +
                              Rainfall_cm +
                              TempMax + 
                              MonthlyFruitBiomass +
                              offset(log(TotalForagingScans)) + 
                              (1 | Group/Animal), 
                              data = dfzGrouped,
                              family = poisson(link = "log"),
                              glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))

summary(fruitModel)
drop1(fruitModel, test = "Chisq")
Anova(fruitModel)

fruitModel.emm <- (emmeans(fruitModel, "ReproductiveStatus", type = "response", adjust = "tukey"))
pairs(fruitModel.emm)
plot(fruitModel.emm, comparisons = TRUE, alpha = 0.5)
fruitModel.emm.cld.tukey <- cld(fruitModel.emm, alpha = 0.05, Letters = letters, adjust = "tukey")
FrM <- fruitModel.emm.cld.tukey

FrM.plot <-    ggplot(FM, aes(x = ReproductiveStatus, y = rate, label = .group)) +
              geom_point(shape = 16, size = 4) +
              geom_errorbar(aes(ymin = rate - SE, ymax = rate + SE), width = 0.2, size = 0.7) +
              scale_y_continuous(limits = c(0, 15)) +
              theme_bw() +
              labs(x = "", y = "Estimated Marginal Means (Mean Fruit Forage Scans)\n") ;FrM.plot
              #ggtitle("Estimated Marginal Means for Foraging Scans\n in Response to Reproductive Status") +
              #theme(plot.title = element_text(lineheight = .8, face = "bold", hjust = 0.5)) 

```

